### 2014-04-25 Response_to_R0_Reviews.tex

    ARFI resolution within a native imaging frame is not considered a limiting
    factor in our ability to delineate the prostate central glands since the
    scan-conversion and slice decimation introduce resolution distortions that
    are at least an order-of-magnitude larger than our native image plane
    resolution.  ARFI image resolution would be a more realistic limiting
    factor if we were using those primary imaging frames for exclusive gland
    delineation, but our use of the 3 orthogonal planes for segmentation makes
    this resolution of higher-order parameter.  We have added to the following
    text to Section V to emphasize this point to the reader:

    \input{arfi_resolution}

    \item \textit{The authors explain that gross pathology weights and axis
            measurements were affected by the presence of peri-prostatic
            tissue.  Why could the peri-prostatic tissue not be differentiated
            from the prostatic tissue in histology after processing?  Wouldn't
            this enable better gold standard axis measurements?}

    The extraprostatic tissue that is left on the prostate by the surgeon is
    usually minimal, but can vary case-by-case and is left in place during
    gross and histologic processing to adhere to AJCC guidelines that require
    the reporting of potential extraprostatic invasion of malignany tumors.
    This extraprostatic tissue is left in place during whole-mount histology
    processing, but given the challenges in estimating prostate gland size post
    histologic processing (detailed in the response to the second reviewer
    below), our pathologist (AB) believed that the most accurate estimations of
    \invivo prostate dimensions would be taken from the gross pathology
    specimens.

    We have modified the text in the Limitations section as follows:

    \textbf{Gross pathology weight and axis measurements could both be affected
        by the presence of extraprostatic tissue that was excised during
        radical prostatectomy, especially in cases where more aggressive
        margins may have been necessary; however, we still believe that these
        weights and measurements represent the best estimation of \invivo
        characteristics.}

### 2014-04-25 limitations.tex
updated extraprostatic text based on more recs from Andrew

\subsection{Limitations}
This study has several limitations that should be considered when interpreting
these results.  Gross pathology weight and axis measurements could both be
affected by the presence of peri-prostatic tissue that was excised during
radical prostatectomy, especially in cases where more aggressive margins may
have been necessary.  For this reason, unlike the image-to-image measurement
comparisons, all of the image metrics presented relative to pathology metrics
(Figure~\ref{fig:mr_arfi_weight}) were not characterized for absolute accuracy,
but instead, relative correlations were evaluated.  Additionally, the volumes
of the prostate from gross pathologic measurements were approximated as
ellipsoids, which also introduced error, most likely an over-estimation of
volume.  Interestingly, all pathology estimates were thought to have positive
biases, but both imaging modalities tended to overestimate volume relative to
the pathology measurements.

>>>>

\subsection{Limitations}
This study has several limitations that should be considered when interpreting
these results.  \textbf{Gross pathology weight and axis measurements could both
be affected by the presence of extraprostatic tissue that was excised during
radical prostatectomy, especially in cases where more aggressive margins may
have been necessary; however, we still believe that these weights and
measurements represent the best estimation of \invivo characteristics.}  For
this reason, unlike the image-to-image measurement comparisons, all of the
image metrics presented relative to pathology metrics
(Figure~\ref{fig:mr_arfi_weight}) were not characterized for absolute accuracy,
but instead, relative correlations were evaluated.  Additionally, the volumes
of the prostate from gross pathologic measurements were approximated as
ellipsoids, which also introduced error, most likely an over-estimation of
volume.  Interestingly, all pathology estimates were thought to have positive
biases, but both imaging modalities tended to overestimate volume relative to
the pathology measurements.
